Stimuli Selection

### 2025-01-27 study2/experiment/stimuli_selection/selection.qmd
Update selection.qmd

# last selection 
last_selection <- selection |>
  filter(!(Category == "Opposite-sex Couple" & total_arousal < 8.8)) |>
  filter(!(ID %in% remove_image))

write.csv(last_selection, "stimuli_data.csv", row.names=FALSE)
knitr::kable(selection)
```

```{r}
#| code-fold: true
json <- last_selection |> 
  select(stimulus=ID, Category, Orientation) |> 
  jsonlite::toJSON()

@@

```{r}
#| code-fold: true
path_ero <- "C:/Users/asf25/OneDrive - University of Sussex/phd/data_base/naps/NAPS_ERO/"

>>>>

# last selection 
selection <- selection |>
  filter(!(Category == "Opposite-sex Couple" & total_arousal < 8.8)) |>
  filter(!(ID %in% remove_image))

write.csv(selection, "stimuli_data.csv", row.names=FALSE)
knitr::kable(selection)
```

```{r}
#| code-fold: true
json <- selection |> 
  select(stimulus=ID, Category, Orientation) |> 
  jsonlite::toJSON()

@@

```{r}
#| code-fold: true
path_ero <- "C:/Users/asf25/Desktop/PhD/data_base/NAPS_ERO/"
